Approximation as Differentiation

### 2025-04-01 notes/sec/cmon-enriched.tex
Defining your 'basic' Yoneda embedding.

$\CMon$ is closed monoidal, and so enriched over itself. More specifically every hom-object $\CMon(A,B)$ is a
commutative monoid of commutative monoid homomorphisms where:

@@

For any monoidal category $V$ and $V$-enriched categories $C$ and $D$, the action of a \emph{$V$-enriched}
functor $F: C \to D$ on morphisms takes the form of a morphism $C(X,Y) \to D(F(X),F(Y))$ between hom-monoids
in $V$. In the specific setting of a $\CMon$-enriched presheaf $F: C^\op \to \CMon$, this means that $F$
preserves the additive structure of morphisms:
\begin{itemize}
\item $F(0_{X,Y}) = 0_{F(Y),F(X)}$
\item $F(f + g) = F(f) + F(g)$
\end{itemize}
It then follows automatically that $F$ also preserves bilinear composition, i.e.:
\begin{itemize}
\item $F(f) \comp F(0) = F(f) = F(0) \comp F(f)$
\item $F(f + g) \comp F(h) = F(h \comp f) + F(h \comp g)$
\item $F(h) \comp F(f + g) = F(f \comp h) + F(g \comp h)$
\end{itemize}
in addition to the usual functorial properties.

@@

Suppose $C$ a small category. The standard \emph{Yoneda embedding} for $C$ is the functor $\Yoneda: C \to
\Func{C^\op}{\Set}$ sending:
\begin{itemize}
\item any object $X$ in $C$ to the contravariant hom-functor $C(-,X)$ which sends:
\begin{itemize}
\item any object $Y$ in $C$ to the hom-set $C(Y,X)$
\item any morphism $f: Y \to Z$ in $C$ to the pre-composition function $(- \comp f): C(Z,X) \to C(Y,X)$
\end{itemize}
\item any morphism $f: X \to Y$ in $C$ to the natural transformation
\end{itemize}

>>>>

$\CMon$ is closed monoidal, and so enriched over itself. More specifically every hom-object $\Hom{CMon}{A}{B}$
is a commutative monoid of commutative monoid homomorphisms where:

@@

For any monoidal category $V$ and $V$-enriched categories $C$ and $D$, the action of a \emph{$V$-enriched}
functor $F: C \to D$ on morphisms takes the form of a morphism $\Hom{C}{X}{Y} \to \Hom{D}{F(X)}{F(Y)}$ between
hom-monoids in $V$. In the specific setting of a $\CMon$-enriched presheaf $F: C^\op \to \CMon$, this means
that $F$ preserves the additive structure of morphisms:
\begin{itemize}
\item $F(0_{X,Y}) = 0_{F(Y),F(X)}$
\item $F(f + g) = F(f) + F(g)$
\end{itemize}
It then follows automatically that $F$ also preserves bilinear composition, i.e.:
\begin{itemize}
\item $F(f) \comp F(0) = F(f) = F(0) \comp F(f)$
\item $F(f + g) \comp F(h) = F(h \comp f) + F(h \comp g)$
\item $F(h) \comp F(f + g) = F(f \comp h) + F(g \comp h)$
\end{itemize}
in addition to the usual functorial properties.

@@

Suppose $C$ a small category. The standard \emph{Yoneda embedding} for $C$ is the functor $\Yoneda: C \to
\Func{C^\op}{\Set}$ sending:
\begin{itemize}
\item any object $X$ in $C$ to the contravariant hom-functor $\Yoneda(X) = \Hom{C}{-}{X}$ which sends:
\begin{itemize}
\item any object $Y$ in $C$ to the hom-set $\Hom{C}{Y}{X}$;
\item any morphism $f: Y \to Z$ in $C$ to the function $\Hom{C}{f}{X} = (- \comp f): \Hom{C}{Z}{X} \to
\Hom{C}{Y}{X}$.
\end{itemize}
\item any morphism $f: X \to Y$ in $C$ to the natural transformation $\Yoneda(f)$ where $\Yoneda(f)_Z = (f
\comp -): \Hom{C}{Z}{X} \to \Hom{C}{Z}{Y}$.
\end{itemize}
